---
title: "SOEP-RKI: Big Five Personality Traits and COVID-19 Antibodies - Modeling Selection"
author: "Michael D. Krämer"
date: "6/10/2021"
output: html_document
---

#### Load packages
```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("DescTools")
library("survey")
library("caret")
```

#### Load merged data set
```{r, echo = T, results = 'hide', warning=FALSE, message=FALSE}
#source("Daten_fuer_mkraemer_MK.R")
load("data/covmerged.rda")
```


#### Inspect data
Merging additional data sets to the original RKI data set introduced missingness for participants who could not be matched with the respective data set. I am not sure why, for example, not all participants could be matched with pgen data. For now, I dealt with this by creating a missingness dummy for each data set that was merged, and recoding NA to 0. 
```{r, warning=FALSE, message=FALSE}
table(covmerged$missing_pl)
table(covmerged$missing_pgen)
table(covmerged$missing_hgen)
table(covmerged$missing_bleib)
table(covmerged$missing_big5)
table(covmerged$missing_covid)
table(covmerged$missing_cluster)
```

#### Remove redundant variables
```{r, warning=FALSE, message=FALSE}
# first, remove variables with var=0
covmerged_red <- covmerged[ - as.numeric(which(apply(covmerged, 2, var) == 0))]

# second, remove highly correlated variables (>.95)
cormat <- cor(covmerged_red)
cormat[!is.finite(cormat)] <- 0
to_be_removed = caret::findCorrelation(cormat, cutoff=0.95) 
to_be_removed = sort(to_be_removed)
covmerged_red <- covmerged_red[, -c(to_be_removed)]

# add dependent variable back in 
covmerged <- cbind(covmerged_red, ev_gesamt = covmerged$ev_gesamt)
```


#### Run reduced stepwise model first
```{r, warning=FALSE, message=FALSE}
glm_formula_red <- as.formula("ev_gesamt ~ p_health1 + p_health3 + p_health4 + p_health5 + p_politic1 + p_politic2 + p_politic4 + p_healthlow + p_sleeplow + p_helwor1 + p_helwor3 + p_lifelow + p_hipriv + p_partypref + p_familylow + p_future1 + p_future3 + p_future4 + missing_pl")
# full model
mod1_participation_red <- glm(formula=glm_formula_red, 
                              family = binomial(link='logit'), data = covmerged)
summary(mod1_participation_red)
# null model
mod0_participation_red <- glm(ev_gesamt ~ 1, family = binomial(link='logit'), 
                     data = covmerged)
summary(mod0_participation_red)

# run stepwise algorithm
mod_stepwise_red <- step(mod1_participation_red, direction = "both", trace = 1, 
                     scope = list(upper = mod1_participation_red, 
                                  lower = mod0_participation_red))
summary(mod_stepwise_red)
```

#### Run stepwise model
Too many variables... Runs forever.
```{r, warning=FALSE, message=FALSE}
glm_formula <- as.formula("ev_gesamt ~ . - hid - dbs_gesamt")
# full model
mod1_participation <- glm(formula=glm_formula, family = binomial(link='logit'), 
                     data = covmerged)
summary(mod1_participation)
# null model
mod0_participation <- glm(ev_gesamt ~ 1, family = binomial(link='logit'), 
                     data = covmerged)
summary(mod0_participation)

# run stepwise algorithm
#mod_stepwise <- step(mod1_participation, direction = "both", trace = 1, 
#                     scope = list(upper = mod1_participation, 
#                                  lower = mod0_participation))
```

