---
title: "SOEP-RKI: Big Five Personality Traits and COVID-19 Antibodies"
author: "Michael D. Krämer"
date: "6/10/2021"
output: html_document
---

#### Load packages
```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("DescTools")
library("survey")
```

#### Load data
```{r, echo = T, results = 'hide', warning=FALSE, message=FALSE}
source("covid-pers-merge.R") # This executes data import & cleaning.
```

#### Inspect data
This dataset still contains around 3.6% missings for the Big Five. These respondents have never filled out the Big Five (validly). I've now used all available data from 2005-2019 to fill in later missings in the Big Five. The variable *lastwave* shows the most recent wave where a respondent answered the Big Five (at least one item - individual missing Big Five traits are also filled in from earlier waves, though).
```{r, warning=FALSE, message=FALSE}
table(covid_pers$core) # 0 = SOEP-IS, 1 = SOEP-Core
table(covid_pers$core, covid_pers$infekt_pos)
table(covid_pers$core, covid_pers$AK_pos)
summary(covid_pers)
covid_pers %>% group_by(core, lastwave) %>% summarise(obs = n())
```

#### Code education and income
```{r, warning=FALSE, message=FALSE}
covid_pers <- covid_pers %>% mutate(
  edu_school = ifelse(pgcasmin==0 & !is.na(pgcasmin), 1, 0), 
  edu_low = ifelse(pgcasmin %in% c(1,2,4), 1, 0), 
  edu_mid = ifelse(pgcasmin %in% c(3,5,6,7), 1, 0), 
  edu_high = ifelse(pgcasmin %in% c(8,9), 1, 0), 
  edu_na = ifelse(is.na(pgcasmin), 1, 0), 
  inc_2000 = ifelse(hghinc<=2000 & !is.na(hghinc), 1, 0), 
  inc_4000 = ifelse(hghinc>2000 & hghinc<=4000 & !is.na(hghinc), 1, 0), 
  inc_6000 = ifelse(hghinc>4000 & hghinc<=6000 & !is.na(hghinc), 1, 0), 
  inc_rich = ifelse(hghinc>6000 & !is.na(hghinc), 1, 0), 
  inc_na = ifelse(is.na(hghinc), 1, 0)
)
```

#### Descriptive results

Mean differences (with the composite measure, *infekt_pos*)
```{r, warning=FALSE, message=FALSE}
covid_pers %>% filter(!is.na(infekt_pos)) %>% group_by(infekt_pos) %>% 
  summarize(n=n(), m_O = mean(open, na.rm=T), sd_O = sd(open, na.rm=T),
  m_C = mean(cons, na.rm=T), sd_C = sd(cons, na.rm=T),
  m_E = mean(extra, na.rm=T), sd_E = sd(extra, na.rm=T),
  m_A = mean(agree, na.rm=T), sd_A = sd(agree, na.rm=T),
  m_N = mean(neuro, na.rm=T), sd_N = sd(neuro, na.rm=T))
```

Mean differences (with the antibodies test result, *AK_pos*)
```{r, warning=FALSE, message=FALSE}
covid_pers %>% filter(!is.na(AK_pos)) %>% group_by(AK_pos) %>% 
  summarize(n=n(), m_O = mean(open, na.rm=T), sd_O = sd(open, na.rm=T),
  m_C = mean(cons, na.rm=T), sd_C = sd(cons, na.rm=T),
  m_E = mean(extra, na.rm=T), sd_E = sd(extra, na.rm=T),
  m_A = mean(agree, na.rm=T), sd_A = sd(agree, na.rm=T),
  m_N = mean(neuro, na.rm=T), sd_N = sd(neuro, na.rm=T))
```

### Main analyses

Main analysis with the composite measure (*infekt_pos*).

#### Start with age and gender

##### Unweighted
```{r, warning=FALSE, message=FALSE}
covid_pers <- covid_pers %>% mutate(female = sex-1)

m1_logit_comp <- glm(infekt_pos ~ female + age, family = binomial(link='logit'), data = covid_pers)
summary(m1_logit_comp)
```

##### Weighted
```{r, warning=FALSE, message=FALSE}
m1_logit_comp_weighted <- svyglm(infekt_pos ~ female + age, design=svydesign(id=~1, weights=~phrf_20_final, data=covid_pers), family=quasibinomial(link='logit')) 
summary(m1_logit_comp_weighted)
```

#### Add other control variables

As reference categories, I chose 'edu_mid' and 'inc_4000' because these were the most frequent categories.

##### Unweighted
```{r, warning=FALSE, message=FALSE}
m2_logit_comp <- glm(infekt_pos ~ female + age + hhgr + edu_school + edu_low + edu_high + edu_na + 
                       inc_2000 + inc_6000 + inc_rich + inc_na, family = binomial(link='logit'), data = covid_pers)
summary(m2_logit_comp)
```

##### Weighted
```{r, warning=FALSE, message=FALSE}
m2_logit_comp_weighted <- svyglm(infekt_pos ~ female + age + hhgr + edu_school + edu_low + edu_high + edu_na + inc_2000 + inc_6000 + inc_rich + inc_na, design=svydesign(id=~1, weights=~phrf_20_final, data=covid_pers), family=quasibinomial(link='logit')) 
summary(m2_logit_comp_weighted)
```

#### Add Big Five traits

##### Unweighted
```{r, warning=FALSE, message=FALSE}
m3_logit_comp <- glm(infekt_pos ~ female + age + hhgr + edu_school + edu_low + edu_high + edu_na + 
                       inc_2000 + inc_6000 + inc_rich + inc_na + open + cons + extra + agree + neuro, family = binomial(link='logit'), data = covid_pers)
summary(m3_logit_comp)
```

##### Weighted
```{r, warning=FALSE, message=FALSE}
m3_logit_comp_weighted <- svyglm(infekt_pos ~ female + age + hhgr + edu_school + edu_low + edu_high +
                                   edu_na + inc_2000 + inc_6000 + inc_rich + inc_na + open + cons + 
                                   extra + agree + neuro, design=svydesign(id=~1, weights=~phrf_20_final, data=covid_pers), family=quasibinomial(link='logit'))
summary(m3_logit_comp_weighted)
```

#### Zero-order models

##### Unweighted
```{r, warning=FALSE, message=FALSE}
open_logit_comp <- glm(infekt_pos ~ open, family = binomial(link='logit'), data = covid_pers)
open_logit_comp_summary <- summary(open_logit_comp)
cons_logit_comp <- glm(infekt_pos ~ cons, family = binomial(link='logit'), data = covid_pers)
cons_logit_comp_summary <- summary(cons_logit_comp)
extra_logit_comp <- glm(infekt_pos ~ extra, family = binomial(link='logit'), data = covid_pers)
extra_logit_comp_summary <- summary(extra_logit_comp)
agree_logit_comp <- glm(infekt_pos ~ agree, family = binomial(link='logit'), data = covid_pers)
agree_logit_comp_summary <- summary(agree_logit_comp)
neuro_logit_comp <- glm(infekt_pos ~ neuro, family = binomial(link='logit'), data = covid_pers)
neuro_logit_comp_summary <- summary(neuro_logit_comp)

# Openness to Experience
round(open_logit_comp_summary$coefficients, 3)
# Conscientiousness
round(cons_logit_comp_summary$coefficients, 3)
# Extraversion
round(extra_logit_comp_summary$coefficients, 3)
# Agreeableness
round(agree_logit_comp_summary$coefficients, 3)
# Neuroticism
round(neuro_logit_comp_summary$coefficients, 3)
```

##### Weighted
```{r, warning=FALSE, message=FALSE}
open_logit_comp_weighted <- svyglm(infekt_pos ~ open, design=svydesign(id=~1, weights=~phrf_20_final, data=covid_pers), family=quasibinomial(link='logit'))
open_logit_comp_weighted_summary <- summary(open_logit_comp_weighted)
cons_logit_comp_weighted <- svyglm(infekt_pos ~ cons, design=svydesign(id=~1, weights=~phrf_20_final, data=covid_pers), family=quasibinomial(link='logit'))
cons_logit_comp_weighted_summary <- summary(cons_logit_comp_weighted)
extra_logit_comp_weighted <- svyglm(infekt_pos ~ extra, design=svydesign(id=~1, weights=~phrf_20_final, data=covid_pers), family=quasibinomial(link='logit'))
extra_logit_comp_weighted_summary <- summary(extra_logit_comp_weighted)
agree_logit_comp_weighted <- svyglm(infekt_pos ~ agree, design=svydesign(id=~1, weights=~phrf_20_final, data=covid_pers), family=quasibinomial(link='logit'))
agree_logit_comp_weighted_summary <- summary(agree_logit_comp_weighted)
neuro_logit_comp_weighted <- svyglm(infekt_pos ~ neuro, design=svydesign(id=~1, weights=~phrf_20_final, data=covid_pers), family=quasibinomial(link='logit'))
neuro_logit_comp_weighted_summary <- summary(neuro_logit_comp_weighted)

# Openness to Experience
round(open_logit_comp_weighted_summary$coefficients, 3)
# Conscientiousness
round(cons_logit_comp_weighted_summary$coefficients, 3)
# Extraversion
round(extra_logit_comp_weighted_summary$coefficients, 3)
# Agreeableness
round(agree_logit_comp_weighted_summary$coefficients, 3)
# Neuroticism
round(neuro_logit_comp_weighted_summary$coefficients, 3)
```

### Model diagnostics

```{r, warning=FALSE, message=FALSE}
DescTools::PseudoR2(m3_logit_comp, which="all")
```
Recommended Pseudo $R^2$ measures: McFadden non-adjusted and adjusted, Tjur's D

To be added: 'LogisticsDx' package not available for this R version. Hosmer-Lemeshow test, Osius-Rajek Standardized Pearson Test, Stukel test.

Calibration Plot in 'rms' package
```{r, warning=FALSE, message=FALSE, fig.height=6, fig.width=6}
library("rms")
rms.out=lrm(infekt_pos ~ female + age + hhgr + edu_school + edu_low + edu_high + edu_na + 
                       inc_2000 + inc_6000 + inc_rich + inc_na + open + cons + extra + agree + neuro, data=covid_pers,x=TRUE,y=TRUE)
plot(calibrate(rms.out))
```

### Secondary analyses

Secondary analyses just with the antibodies measure (*AK_pos*) - not including PCR test results and self-reported infections.

#### Start with age and gender

##### Unweighted
```{r, warning=FALSE, message=FALSE}
m1_logit_anti <- glm(AK_pos ~ female + age, family = binomial(link='logit'), data = covid_pers)
summary(m1_logit_anti)
```

##### Weighted
```{r, warning=FALSE, message=FALSE}
# apparently I need a version of the dataset without missings in the weighting variable
covid_pers_AK_only <- covid_pers %>% filter(!is.na(AK_pos))

m1_logit_anti_weighted <- svyglm(AK_pos ~ female + age, design=svydesign(id=~1, weights=~phrf_20_final_dbs, data=covid_pers_AK_only), family=quasibinomial(link='logit'))
summary(m1_logit_anti_weighted)
```

#### Add other control variables

As reference categories, I chose 'edu_mid' and 'inc_4000' because these were the most frequent categories.

##### Unweighted
```{r, warning=FALSE, message=FALSE}
m2_logit_anti <- glm(AK_pos ~ female + age + hhgr + edu_school + edu_low + edu_high + edu_na + 
                       inc_2000 + inc_6000 + inc_rich + inc_na, family = binomial(link='logit'), data = covid_pers)
summary(m2_logit_anti)
```

##### Weighted
```{r, warning=FALSE, message=FALSE}
m2_logit_anti_weighted <- svyglm(AK_pos ~ female + age + hhgr + edu_school + edu_low + edu_high + edu_na + 
                       inc_2000 + inc_6000 + inc_rich + inc_na, design=svydesign(id=~1, weights=~phrf_20_final_dbs, data=covid_pers_AK_only), family=quasibinomial(link='logit'))
summary(m2_logit_anti_weighted)  
```

#### Add Big Five traits

##### Unweighted
```{r, warning=FALSE, message=FALSE}
m3_logit_anti <- glm(AK_pos ~ female + age + hhgr + edu_school + edu_low + edu_high + edu_na + 
                       inc_2000 + inc_6000 + inc_rich + inc_na + open + cons + extra + agree + neuro, family = binomial(link='logit'), data = covid_pers)
summary(m3_logit_anti)
```

##### Weighted
```{r, warning=FALSE, message=FALSE}
m3_logit_anti_weighted <- svyglm(AK_pos ~ female + age + hhgr + edu_school + edu_low + edu_high + edu_na + 
                       inc_2000 + inc_6000 + inc_rich + inc_na + open + cons + extra + agree + neuro, design=svydesign(id=~1, weights=~phrf_20_final_dbs, data=covid_pers_AK_only), family=quasibinomial(link='logit'))
summary(m3_logit_anti_weighted)  
```

#### Zero-order models

##### Unweighted
```{r, warning=FALSE, message=FALSE}
open_logit_anti <- glm(AK_pos ~ open, family = binomial(link='logit'), data = covid_pers)
open_logit_anti_summary <- summary(open_logit_anti)
cons_logit_anti <- glm(AK_pos ~ cons, family = binomial(link='logit'), data = covid_pers)
cons_logit_anti_summary <- summary(cons_logit_anti)
extra_logit_anti <- glm(AK_pos ~ extra, family = binomial(link='logit'), data = covid_pers)
extra_logit_anti_summary <- summary(extra_logit_anti)
agree_logit_anti <- glm(AK_pos ~ agree, family = binomial(link='logit'), data = covid_pers)
agree_logit_anti_summary <- summary(agree_logit_anti)
neuro_logit_anti <- glm(AK_pos ~ neuro, family = binomial(link='logit'), data = covid_pers)
neuro_logit_anti_summary <- summary(neuro_logit_anti)

# Openness to Experience
round(open_logit_anti_summary$coefficients, 3)
# Conscientiousness
round(cons_logit_anti_summary$coefficients, 3)
# Extraversion
round(extra_logit_anti_summary$coefficients, 3)
# Agreeableness
round(agree_logit_anti_summary$coefficients, 3)
# Neuroticism
round(neuro_logit_anti_summary$coefficients, 3)
```

##### Weighted
```{r, warning=FALSE, message=FALSE}
open_logit_anti_weighted <- svyglm(AK_pos ~ open, design=svydesign(id=~1, weights=~phrf_20_final_dbs, data=covid_pers_AK_only), family=quasibinomial(link='logit'))
open_logit_anti_weighted_summary <- summary(open_logit_anti_weighted)
cons_logit_anti_weighted <- svyglm(AK_pos ~ cons, design=svydesign(id=~1, weights=~phrf_20_final_dbs, data=covid_pers_AK_only), family=quasibinomial(link='logit'))
cons_logit_anti_weighted_summary <- summary(cons_logit_anti_weighted)
extra_logit_anti_weighted <- svyglm(AK_pos ~ extra, design=svydesign(id=~1, weights=~phrf_20_final_dbs, data=covid_pers_AK_only), family=quasibinomial(link='logit'))
extra_logit_anti_weighted_summary <- summary(extra_logit_anti_weighted)
agree_logit_anti_weighted <- svyglm(AK_pos ~ agree, design=svydesign(id=~1, weights=~phrf_20_final_dbs, data=covid_pers_AK_only), family=quasibinomial(link='logit'))
agree_logit_anti_weighted_summary <- summary(agree_logit_anti_weighted)
neuro_logit_anti_weighted <- svyglm(AK_pos ~ neuro, design=svydesign(id=~1, weights=~phrf_20_final_dbs, data=covid_pers_AK_only), family=quasibinomial(link='logit'))
neuro_logit_anti_weighted_summary <- summary(neuro_logit_anti_weighted)

# Openness to Experience
round(open_logit_anti_weighted_summary$coefficients, 3)
# Conscientiousness
round(cons_logit_anti_weighted_summary$coefficients, 3)
# Extraversion
round(extra_logit_anti_weighted_summary$coefficients, 3)
# Agreeableness
round(agree_logit_anti_weighted_summary$coefficients, 3)
# Neuroticism
round(neuro_logit_anti_weighted_summary$coefficients, 3)
```

### Model diagnostics

```{r, warning=FALSE, message=FALSE}
DescTools::PseudoR2(m3_logit_anti, which="all")
```
Recommended Pseudo $R^2$ measures: McFadden non-adjusted and adjusted, Tjur's D

To be added: 'LogisticsDx' package not available for this R version. Hosmer-Lemeshow test, Osius-Rajek Standardized Pearson Test, Stukel test.

Calibration Plot in 'rms' package
```{r, warning=FALSE, message=FALSE, fig.height=6, fig.width=6}
library("rms")
rms.out=lrm(AK_pos ~ female + age + hhgr + edu_school + edu_low + edu_high + edu_na + 
                       inc_2000 + inc_6000 + inc_rich + inc_na + open + cons + extra + agree + neuro, data=covid_pers,x=TRUE,y=TRUE)
plot(calibrate(rms.out))
```

### Exclude Federal States

As preregistered, we exclude participants from three federal states with very low reported coronavirus case numbers: Brandenburg, Sachsen-Anhalt, and Mecklenburg-Vorpommern.

##### Unweighted
```{r, warning=FALSE, message=FALSE}
# exclude via 'bula'
covid_pers_bula <- covid_pers %>% filter(bula %in% c(1:11,15:16))

m3_logit_comp_bula <- glm(infekt_pos ~ female + age + hhgr + edu_school + edu_low + edu_high + edu_na + 
                       inc_2000 + inc_6000 + inc_rich + inc_na + open + cons + extra + agree + neuro, family = binomial(link='logit'), data = covid_pers_bula)
summary(m3_logit_comp_bula)

m3_logit_anti_bula <- glm(AK_pos ~ female + age + hhgr + edu_school + edu_low + edu_high + edu_na + 
                       inc_2000 + inc_6000 + inc_rich + inc_na + open + cons + extra + agree + neuro, family = binomial(link='logit'), data = covid_pers_bula)
summary(m3_logit_anti_bula)
```

##### Weighted
```{r, warning=FALSE, message=FALSE}
# exclude via 'bula'
covid_pers_AK_only_bula <- covid_pers_AK_only %>% filter(bula %in% c(1:11,15:16))

m3_logit_comp_bula_weighted <- svyglm(infekt_pos ~ female + age + hhgr + edu_school + edu_low + edu_high + 
                                        edu_na + inc_2000 + inc_6000 + inc_rich + inc_na + open + cons +
                                        extra + agree + neuro, design=svydesign(id=~1, weights=~phrf_20_final, data=covid_pers_bula), family=quasibinomial(link='logit'))
summary(m3_logit_comp_bula_weighted)

m3_logit_anti_bula_weighted <- svyglm(AK_pos ~ female + age + hhgr + edu_school + edu_low + edu_high + 
                                        edu_na + inc_2000 + inc_6000 + inc_rich + inc_na + open + cons +
                                        extra + agree + neuro, design=svydesign(id=~1, weights=~phrf_20_final_dbs, data=covid_pers_AK_only_bula), family=quasibinomial(link='logit'))
summary(m3_logit_anti_bula_weighted)  
```

### To Be Done (?)

* Imputations?
* "For the same reason, in another additional analysis, we plan to exclude participants who indicated to have mostly worked from home during the coronavirus crisis."
* "Lastly, due to the rising incidence rates in Germany during the field phase we will analyze timing of the administration of the antibody tests (measured by postal return date) as a moderator by comparing effects in the first third of all conducted test against effects in the last third of all conducted tests."