---
title: "SOEP-RKI: Big Five Personality Traits and COVID-19 Antibodies - Modeling Selection"
author: "Michael D. Krämer"
date: "6/10/2021"
output: html_document
---

#### Load packages
```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("DescTools")
library("survey")
library("caret")
library("randomForest")
```

#### Load merged data set
```{r, echo = T, results = 'hide', warning=FALSE, message=FALSE}
#source("Daten_fuer_mkraemer_MK.R")
load("data/covmerged.rda")
```


#### Inspect data
Merging additional data sets to the original RKI data set introduced missingness for participants who could not be matched with the respective data set. I am not sure why, for example, not all participants could be matched with pgen data. For now, I dealt with this by creating a missingness dummy for each data set that was merged, and recoding NA to 0. 
```{r, warning=FALSE, message=FALSE}
table(covmerged$missing_pl)
table(covmerged$missing_pgen)
table(covmerged$missing_hgen)
table(covmerged$missing_bleib)
table(covmerged$missing_big5)
table(covmerged$missing_covid)
table(covmerged$missing_cluster)
```

#### Remove redundant variables
```{r, warning=FALSE, message=FALSE}
# first, remove variables with var=0
covmerged_red <- covmerged[ - as.numeric(which(apply(covmerged, 2, var) == 0))]

# second, remove highly correlated variables (>.90)
cormat <- cor(covmerged_red)
cormat[!is.finite(cormat)] <- 0
to_be_removed = caret::findCorrelation(cormat, cutoff=0.90) 
to_be_removed = sort(to_be_removed)
covmerged_red <- covmerged_red[, -c(to_be_removed)]

# add dependent variable back in 
covmerged <- cbind(covmerged_red, ev_gesamt = covmerged$ev_gesamt)
covmerged <- covmerged %>% mutate(ev_gesamt_fac = as.factor(ev_gesamt)) # needed for random forest
```


#### Run stepwise model
Too many variables... Runs forever.
```{r, warning=FALSE, message=FALSE}
glm_formula <- as.formula("ev_gesamt ~ . - hid - dbs_gesamt")
# full model
mod1_participation <- glm(formula=glm_formula, family = binomial(link='logit'), 
                     data = covmerged)
#summary(mod1_participation)
# null model
mod0_participation <- glm(ev_gesamt ~ 1, family = binomial(link='logit'), 
                     data = covmerged)
#summary(mod0_participation)

# run stepwise algorithm
#mod_stepwise <- step(mod1_participation, direction = "both", trace = 1, 
#                     scope = list(upper = mod1_participation, 
#                                  lower = mod0_participation))
```

#### Random forest - variable importance
Information on function: https://www.rdocumentation.org/packages/randomForest/versions/4.6-14/topics/importance  
Some basic information on method: https://www.r-bloggers.com/2015/06/variable-importance-plot-and-variable-selection/  
https://www.stat.berkeley.edu/~breiman/RandomForests/cc_home.htm#varimp
```{r, warning=FALSE, message=FALSE, cache=T}
covmerged <- covmerged %>% select(-ev_gesamt)
cov.rf <- randomForest(ev_gesamt_fac ~ ., data=covmerged, ntree=1000,
                          keep.forest=FALSE, importance=TRUE)
#importance(cov.rf)

imp_cov <- as.data.frame(importance(cov.rf))
# 'MeanDecreaseGini' is the relevant measure for variable importance
imp_cov %>% arrange(desc(MeanDecreaseGini)) %>% slice(1:20)
```



