---
title: "SOEP-RKI: Big Five Personality Traits and COVID-19 Antibodies - Modeling Selection"
author: "Michael D. Krämer"
date: "6/10/2021"
output: html_document
---

#### Load packages
```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("DescTools")
library("survey")
```

#### Load individual data sets
```{r, echo = T, results = 'hide', warning=FALSE, message=FALSE}

```



#### Inspect data
This dataset still contains around 3.6% missings for the Big Five. These respondents have never filled out the Big Five (validly). I've now used all available data from 2005-2019 to fill in later missings in the Big Five. The variable *lastwave* shows the most recent wave where a respondent answered the Big Five (at least one item - individual missing Big Five traits are also filled in from earlier waves, though).
```{r, warning=FALSE, message=FALSE}
table(covid_pers$core) # 0 = SOEP-IS, 1 = SOEP-Core
table(covid_pers$core, covid_pers$infekt_pos)
table(covid_pers$core, covid_pers$AK_pos)
summary(covid_pers)
covid_pers %>% group_by(core, lastwave) %>% summarise(obs = n())
```
